<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-10-26 MainAnalysis.Rmd
Most of MainAnalysis.Rmd working now

```{r, include = FALSE}
library(tidyverse)
library(data.table)
library(readxl)
devtools::load_all(".")
```

@@

```{r, plot_1comp, eval=TRUE}
plot_conctime(PK.fit.table.1comp[[1]],cvt.data,"1compartment")
head(subset(PK.fit.table.1comp[[1]],Vdist>10000&!is.infinite(AIC)&param.value.type=="Fitted geometric mean"))
```

```{r, run_invivoPKfit_2comp, eval = TRUE}
### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = cvt.data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))
```

```{r, run_invivoPKfit_flat, eval = TRUE}
### do flat fit
system.time(PK.fit.table.flat <- fit_all(
  data.set = cvt.data,
  model = "flat",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))

### uncomment below to export to CSV files
# change the date!!

write.csv(PK.fit.table.1comp[[1]], paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
write.csv(PK.fit.table.1comp[[2]], paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)

@@

### read in PK output files
# pk_output_1comp_12212021 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv")
# pk_output_2comp_02102022 <- read.csv("inst/ext/PK.fit.table.2comp.02102022.csv")
# pk_output_flat_02102022 <- read.csv("inst/ext/PK.fit.table.flat.02102022.csv")

# pk_output_1comp_03012022 <- read.csv("inst/ext/PK.fit.table.1comp.03012022.csv")
# pk_output_2comp_03012022<- read.csv("inst/ext/PK.fit.table.2comp.03012022.csv")
# pk_output_flat_03012022 <- read.csv("inst/ext/PK.fit.table.flat.03012022.csv")

pk_output_1comp_04282022 <- read.csv("inst/ext/PK.fit.table.1comp.04282022.csv")
pk_output_2comp_04282022<- read.csv("inst/ext/PK.fit.table.2comp.04282022.csv")
pk_output_flat_04282022 <- read.csv("inst/ext/PK.fit.table.flat.04282022.csv")

pk_output_2comp_05092022 <- read.csv("inst/ext/PK.fit.table.2comp.05092022.csv")
pk_output_flat_05092022 <- read.csv("inst/ext/PK.fit.table.flat.05092022.csv")
pk_output_1comp_05092022 <- read.csv("inst/ext/PK.fit.table.1comp.05092022.csv")

### read in processed raw data files
# raw_1comp_12212021 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
# raw_2comp_02102022 <- read.csv("inst/ext/processed.2comp.data.02102022.csv")
# raw_flat_02102022 <- read.csv("inst/ext/processed.flat.data.02102022.csv")

# raw_1comp_03012022 <- read.csv("inst/ext/processed.1comp.data.03012022.csv")
# raw_2comp_03012022 <- read.csv("inst/ext/processed.2comp.data.03012022.csv")
# raw_flat_03012022 <- read.csv("inst/ext/processed.flat.data.03012022.csv")

# raw_1comp_04142022 <- read.csv("inst/ext/processed.1comp.data.04142022.csv")
# raw_2comp_04142022 <- read.csv("inst/ext/processed.2comp.data.04142022.csv")
# raw_flat_04142022 <- read.csv("inst/ext/processed.flat.data.04142022.csv")

raw_1comp_04282022 <- read.csv("inst/ext/processed.1comp.data.04282022.csv")
raw_2comp_04282022 <- read.csv("inst/ext/processed.2comp.data.04282022.csv")
raw_flat_04282022 <- read.csv("inst/ext/processed.flat.data.04282022.csv")

raw_1comp_05092022 <- read.csv("inst/ext/processed.1comp.data.05092022.csv")
raw_2comp_05092022 <- read.csv("inst/ext/processed.2comp.data.05092022.csv")
raw_flat_05092022 <- read.csv("inst/ext/processed.flat.data.05092022.csv")

@@

### save data
# save(pk_output_1comp_12212021, file = "figures_rdata/pk_output_1comp_12212021.Rdata")
# save(pk_output_2comp_02102022, file = "figures_rdata/pk_output_2comp_12212021.Rdata")
# save(pk_output_flat_02102022, file = "figures_rdata/pk_output_flat_02102022.Rdata")
# save(raw_1comp_12212021, file = "figures_rdata/raw_1comp_12212021.Rdata")
# save(raw_2comp_02102022, file = "figures_rdata/raw_2comp_12212021.Rdata")
# save(raw_flat_02102022, file = "figures_rdata/raw_flat_02102022.Rdata")

# save(pk_output_1comp_03012022, file = "figures_rdata/pk_output_1comp_03012022.Rdata")
# save(pk_output_2comp_03012022, file = "figures_rdata/pk_output_2comp_03012022.Rdata")
# save(pk_output_flat_03012022, file = "figures_rdata/pk_output_flat_03012022.Rdata")
# save(raw_1comp_03012022, file = "figures_rdata/raw_1comp_03012022.Rdata")
# save(raw_2comp_03012022, file = "figures_rdata/raw_2comp_03012022.Rdata")
# save(raw_flat_03012022, file = "figures_rdata/raw_flat_03012022.Rdata")

# save(pk_output_1comp_04142022, file = "figures_rdata/pk_output_1comp_04142022.Rdata")
# save(pk_output_2comp_04142022, file = "figures_rdata/pk_output_2comp_04142022.Rdata")
# save(pk_output_flat_04142022, file = "figures_rdata/pk_output_flat_04142022.Rdata")
# save(raw_1comp_04142022, file = "figures_rdata/raw_1comp_04142022.Rdata")
# save(raw_2comp_04142022, file = "figures_rdata/raw_2comp_04142022.Rdata")
# save(raw_flat_04142022, file = "figures_rdata/raw_flat_04142022.Rdata")

save(pk_output_1comp_05092022, file = "figures_rdata/pk_output_1comp_05092022.Rdata")
save(pk_output_2comp_05092022, file = "figures_rdata/pk_output_2comp_05092022.Rdata")
save(pk_output_flat_05092022, file = "figures_rdata/pk_output_flat_05092022.Rdata")
save(raw_1comp_05092022, file = "figures_rdata/raw_1comp_05092022.Rdata")
save(raw_2comp_05092022, file = "figures_rdata/raw_2comp_05092022.Rdata")
save(raw_flat_05092022, file = "figures_rdata/raw_flat_05092022.Rdata")

save(pk_lombardo, file = "figures_rdata/pk_lombardo_02072022.Rdata")
```

### load all of this wonderful data
# load("figures_rdata/pk_output_1comp_12212021.Rdata")
# load("figures_rdata/pk_output_2comp_12212021.Rdata")
# load("figures_rdata/raw_1comp_12212021.Rdata")
# load("figures_rdata/raw_2comp_12212021.Rdata")
# load("figures_rdata/cp_df_12212021.Rdata")
# load("figures_rdata/cvt_variability_df_12212021.Rdata")

# load("figures_rdata/pk_output_1comp_03012022.Rdata")
# load("figures_rdata/pk_output_2comp_03012022.Rdata")
# load("figures_rdata/pk_output_flat_03012022.Rdata")
# load("figures_rdata/raw_1comp_03012022.Rdata")
# load("figures_rdata/raw_2comp_03012022.Rdata")
# load("figures_rdata/raw_flat_03012022.Rdata")
# load("figures_rdata/cp_df_03012022.Rdata")
# load("figures_rdata/cvt_variability_df_03012022.Rdata")

# load("figures_rdata/pk_output_1comp_04142022.Rdata")
# load("figures_rdata/pk_output_2comp_04142022.Rdata")
# load("figures_rdata/pk_output_flat_04142022.Rdata")
# load("figures_rdata/raw_1comp_04142022.Rdata")
# load("figures_rdata/raw_2comp_04142022.Rdata")
# load("figures_rdata/raw_flat_04142022.Rdata")
# load("figures_rdata/cp_df_04142022.Rdata")
# load("figures_rdata/cvt_variability_df_04142022.Rdata")
# 
# load("figures_rdata/cp_df_03302022.Rdata")

# load("figures_rdata/pk_output_1comp_04282022.Rdata")
# load("figures_rdata/pk_output_2comp_04282022.Rdata")
# load("figures_rdata/pk_output_flat_04282022.Rdata")
# load("figures_rdata/raw_1comp_04282022.Rdata")
# load("figures_rdata/raw_2comp_04282022.Rdata")
# load("figures_rdata/raw_flat_04282022.Rdata")
# load("figures_rdata/cp_df_04282022.Rdata")
# load("figures_rdata/cvt_variability_df_04282022.Rdata")
# 
# load("figures_rdata/cp_df_04282022.Rdata")

load("figures_rdata/pk_output_1comp_05092022.Rdata")
load("figures_rdata/pk_output_2comp_05092022.Rdata")
load("figures_rdata/pk_output_flat_05092022.Rdata")
load("figures_rdata/raw_1comp_05092022.Rdata")
load("figures_rdata/raw_2comp_05092022.Rdata")
load("figures_rdata/raw_flat_05092022.Rdata")
load("figures_rdata/cp_df_05092022.Rdata")
load("figures_rdata/cvt_variability_df_05092022.Rdata")

load("figures_rdata/cp_df_05092022.Rdata")

```{r, make_invivoPKfit_plots, eval = FALSE}

@@

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data1 <- pk_output_1comp_05092022 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis") %>% 
  filter(Species != "hamster")

raw_data1 <- dplyr::select(raw_1comp_05092022, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs")) %>% 
  filter(Species != "hamster")

@@

cp_df_05092022 <- cp_df

### here is where you save the Rdata file
save(cp_df_05092022, file = "figures_rdata/cp_df_05092022.Rdata")
```

>>>>

```{r, include = FALSE}
library(tidyverse)
library(data.table)
library(readxl)
devtools::load_all("invivopkfit")
```

@@

```{r, plot_1comp, eval=FALSE}
plot_conctime(PK.fit.table.1comp[[1]],cvt.data,"1compartment")
head(subset(PK.fit.table.1comp[[1]],Vdist>10000&!is.infinite(AIC)&param.value.type=="Fitted geometric mean"))
```

```{r, run_invivoPKfit_2comp, eval = TRUE}
### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = cvt.data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))
```
```{r, plot_2comp, eval=FALSE}
plot_conctime(PK.fit.table.2comp[[1]],cvt.data,"2compartment")
head(subset(PK.fit.table.2comp[[1]],Vdist>10000&!is.infinite(AIC)&param.value.type=="Fitted geometric mean"))
```

```{r, run_invivoPKfit_flat, eval = TRUE}
### do flat fit
system.time(PK.fit.table.flat <- fit_all(
  data.set = cvt.data,
  model = "flat",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))
```

```{r, write_invivoPKfits_to_file, eval = TRUE}
write.csv(PK.fit.table.1comp[[1]], paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
write.csv(PK.fit.table.1comp[[2]], paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)

@@

pk_output_2comp <- read.csv(paste("inst/ext/PK.fit.table.2comp.",THIS.DATE,".csv",sep=""))
pk_output_flat <- read.csv(paste("inst/ext/PK.fit.table.flat.",THIS.DATE,".csv",sep=""))
pk_output_1comp <- read.csv(paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""))

raw_1comp <- read.csv(paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""))
raw_2comp <- read.csv(paste("inst/ext/processed.2comp.data.",THIS.DATE,".csv",sep=""))
raw_flat <- read.csv(paste("inst/ext/processed.flat.data.",THIS.DATE,".csv",sep=""))

@@

### save data
paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".RData",sep="")
save(pk_output_1comp, file = paste("figures_rdata/pk_output_1comp_",THIS.DATE,".RData",sep=""))
save(pk_output_2comp, file = paste("figures_rdata/pk_output_2comp_",THIS.DATE,".RData",sep=""))
save(pk_output_flat, file = paste("figures_rdata/pk_output_flat_",THIS.DATE,".RData",sep=""))
save(raw_1comp, file = paste("figures_rdata/raw_1comp_",THIS.DATE,".RData",sep=""))
save(raw_2comp, file = paste("figures_rdata/raw_2comp_",THIS.DATE,".RData",sep=""))
save(raw_flat, file = paste("figures_rdata/raw_flat_",THIS.DATE,".RData",sep=""))

save(pk_lombardo, file = paste("figures_rdata/pk_lombardo",THIS.DATE,".RData",sep=""))
```

```{r, make_invivoPKfit_plots, eval = TRUE}

@@

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data1 <- pk_output_1comp %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis") %>% 
  filter(Species != "hamster")

raw_data1 <- dplyr::select(raw_1comp, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs")) %>% 
  filter(Species != "hamster")

@@

### here is where you save the Rdata file
save(cp_df, file = paste(figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
```

### load all of this wonderful data
load(paste("figures_rdata/pk_output_1comp_",THIS.DATE,".RData",sep=""))
load(paste("figures_rdata/pk_output_2comp_",THIS.DATE,".RData",sep=""))
load(paste("figures_rdata/pk_output_flat_",THIS.DATE,".RData",sep=""))
load(paste("figures_rdata/raw_1comp_",THIS.DATE,".RData",sep=""))
load(paste("figures_rdata/raw_2comp_",THIS.DATE,".RData",sep=""))
load(paste("figures_rdata/raw_flat_",THIS.DATE,".RData",sep=""))
load(paste("figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
load(paste("figures_rdata/cvt_variability_df_",THIS.DATE,".RData",sep=""))

load(paste("figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
